---
title: "French given names per year per department"
author: "Lucas Mello Schnorr, Jean-Marc Vincent"
date: "October, 2022"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# The problem context
The aim of the activity is to develop a methodology to answer a specific question on a given dataset. 

The dataset is the set of Firstname given in France on a large period of time. 
[https://www.insee.fr/fr/statistiques/2540004](https://www.insee.fr/fr/statistiques/fichier/2540004/dpt2021_csv.zip), we choose this dataset because it is sufficiently large, you can't do the analysis by hand, the structure is simple


You need to use the _tidyverse_ for this analysis. Unzip the file _dpt2020_txt.zip_ (to get the **dpt2020.csv**). Read in R with this code. Note that you might need to install the `readr` package with the appropriate command.

## Download Raw Data from the website
```{r}
file = "dpt2021_csv.zip"
if(!file.exists(file)){
  download.file("https://www.insee.fr/fr/statistiques/fichier/2540004/dpt2021_csv.zip",
	destfile=file)
}
unzip(file)
```
Check if your file is the same as in the first analysis (reproducibility)
```{bash}
md5 dpt2021.csv
```
expected :
MD5 (dpt2021.csv) = f18a7d627883a0b248a0d59374f3bab7


## Build the Dataframe from file

```{r}
library(tidyverse)

FirstNames <- read_delim("dpt2021.csv",delim=";")
```

All of these following questions may need a preliminary analysis of the data, feel free to present answers and justifications in your own order and structure your report as it should be for a scientific report.

1. Choose a firstname and analyse its frequency along time. Compare several firstnames frequency

##Creation of a dataframe without na values
```{r}
FirstNames$annais[FirstNames$annais %in% c("XXXX")] <- NA
FirstNames$dpt[FirstNames$dpt %in% c("XX")] <- NA

df <- na.omit(FirstNames)

```

##analyse for 1 firstname -> Zyan
#Creation of table of frequency for ZYAN
```{r}
zyan_freq <- df[df$preusuel == "ZYAN", ]
```

#Creation of the graph depending on the "zyan_freq" table
```{r}
library(ggplot2)

ggplot(zyan_freq, aes(x = annais, y = nombre)) +
  geom_bar(stat = "identity") +
  labs(title = "Frequency of the firstname Zyan depending on the year", x = "Year", y = "Frequency")
```
##Analyse for multiple firstnames --> Zyan, Otto
#Creation table for frequency
```{r}

multiple_freq <- df[df$preusuel %in% c("ZYAN", "OTTO"), ]

```

```{r}
ggplot(multiple_freq, aes(x = annais, y = nombre, fill = preusuel)) +
  geom_bar(stat = "identity") +
  labs(title = "Comparaison of the frequency of the Zyan and Otto name depending on the year", x = "Year", y = "Frequency") +
  scale_fill_discrete(name = "Firstname")
```


2. Establish by gender the most given firstname by year. 

```{r}
library(dplyr)

most_given_names <- df %>%
  group_by(annais, sexe, preusuel) %>%
  summarise(total = sum(nombre), .groups = 'drop') %>%
  group_by(annais, sexe) %>%
  filter(total == max(total)) %>%
  arrange(annais)

print(most_given_names)
```
Analyse the evolution of the most frequent firstname.
```{r}
most_given_name_allyears <- df %>%
  group_by(sexe, preusuel) %>%
  summarise(total = sum(nombre), .groups = 'drop') %>%
  group_by(sexe) %>%
  filter(total == max(total))

most_given_name_allyears <- most_given_name_allyears %>%
  rename(most_given_name = preusuel)

print(most_given_name_allyears)
```
#graph
```{r}

```



3. Optional : Which department has a larger variety of names along time ? Is there some sort of geographical correlation with the data?
